Contextuality and the Born rule in fuzzy quantum theories

### 2017-03-23 prop_letter.tex
prop_letter.tex \paragraph{The Kochen-Specker Theorem} Updating...

On the other hand, Gleason's theorem can be expressed as the limiting
case when the collection of intervals are all singletons~$\mathscr{I}_{\infty}=\set{\left[x,x\right]}{x\in\left[0,1\right]}$.
In the next paragraph, we will show the Kochen-Specker theorem~\citep{kochenspecker1967,peres1995quantum,Redhead1987-REDINA}
is another limiting case when the collection of intervals are $\mathscr{I}_{\mathrm{D}}=\left\{ \imposs,\necess\right\} $,
where $\imposs=\left[0,0\right]$ and $\necess=\left[1,1\right]$.\newpage{}

@@

The Kochen-Specker theorem asserts that there is no function~$v$
assigning a definitely value to all observables such that 
\begin{subequations}
\label{eq:Kochen-Specker-Rules}
\begin{eqnarray}
 &  & v\left(O_{1}\right)+v\left(O_{2}\right)=v\left(O_{1}+O_{2}\right)\textrm{ and}\\
 &  & v\left(O_{1}\right)v\left(O_{2}\right)=v\left(O_{1}O_{2}\right)
\end{eqnarray}
\end{subequations}
if $O_{1}$ and $O_{2}$ are commuting observables. Suppose that
there is a function~$v$ satisfying these two properties, it must send
an observable to its eigenvalues so that the following observables~\cite{Mermin1990Simple,peres1995quantum}:
\begin{equation}
\begin{array}{ccc}
\mathbb{1}\otimes\sigma_{z} & \sigma_{z}\otimes\mathbb{1} & \sigma_{z}\otimes\sigma_{z}\\
\sigma_{x}\otimes\mathbb{1} & \mathbb{1}\otimes\sigma_{x} & \sigma_{x}\otimes\sigma_{x}\\
\sigma_{x}\otimes\sigma_{z} & \sigma_{z}\otimes\sigma_{x} & \sigma_{y}\otimes\sigma_{y}
\end{array}\label{eq:MerminSquare}
\end{equation}
must be sent to $1$ or $-1$. In each row and column, operators commutes,
and each operator is the product of the two others, except in the
third column $\left(\sigma_{z}\otimes\sigma_{z}\right)\left(\sigma_{x}\otimes\sigma_{x}\right)=-\sigma_{y}\otimes\sigma_{y}$.
Therefore, it is clear impossible to find a function~$v$ such that
\begin{equation}
\begin{array}{ccc}
v\left(\mathbb{1}\otimes\sigma_{z}\right) & v\left(\sigma_{z}\otimes\mathbb{1}\right) & v\left(\sigma_{z}\otimes\sigma_{z}\right)\\
v\left(\sigma_{x}\otimes\mathbb{1}\right) & v\left(\mathbb{1}\otimes\sigma_{x}\right) & v\left(\sigma_{x}\otimes\sigma_{x}\right)\\
v\left(\sigma_{x}\otimes\sigma_{z}\right) & v\left(\sigma_{z}\otimes\sigma_{x}\right) & v\left(\sigma_{y}\otimes\sigma_{y}\right)
\end{array}\label{eq:MerminSquare-values}
\end{equation}
satisfying equation~(\ref{eq:Kochen-Specker-Rules}).

\begin{table*}
\caption{\label{table:commonBasis}In each row, three observables are listed
in the left column commutes, and their common eigenbasis is listed
in the right column. In order to unified and simplify notation, we
do not normalize eigenstates, and represent the state~$\alpha_{0}\ket{0}+\alpha_{1}\ket{1}+\alpha_{2}\ket{2}+\alpha_{3}\ket{3}$
as $\left(\alpha_{0},\alpha_{1},\alpha_{2},\alpha_{3}\right)$.}
\begin{ruledtabular}
\begin{tabular}{ccc|cccc} 
\multicolumn{3}{c}{Commuting observables} & \multicolumn{4}{c}{Common eigenbasis} \\
\hline
$\mathbb{1}\otimes\sigma_{z}$ & $\sigma_{z}\otimes\mathbb{1}$ & $\sigma_{z}\otimes\sigma_{z}$ & $(1, 0, 0, 0)$ & $(0, 1, 0, 0)$ & $(0, 0, 1, 0)$ & $(0, 0, 0, 1)$ \\
$\sigma_{x}\otimes\mathbb{1}$ & $\mathbb{1}\otimes\sigma_{x}$ & $\sigma_{x}\otimes\sigma_{x}$ & $(1, 1, 1, 1)$ & $(1, -1, 1, -1)$ & $(1, 1, -1, -1)$ & $(1, -1, -1, 1)$ \\
$\sigma_{x}\otimes\sigma_{z}$ & $\sigma_{z}\otimes\sigma_{x}$ & $\sigma_{y}\otimes\sigma_{y}$ & $(1, 1, 1, -1)$ & $(1, 1, -1, 1)$ & $(1, -1, 1, 1)$ & $(-1, 1, 1, 1)$ \\
$\mathbb{1}\otimes\sigma_{z}$ & $\sigma_{x}\otimes\mathbb{1}$ & $\sigma_{x}\otimes\sigma_{z}$ & $(1, 0, 1, 0)$ & $(0, 1, 0, 1)$ & $(1, 0, -1, 0)$ & $(0, 1, 0, -1)$ \\
$\sigma_{z}\otimes\mathbb{1}$ & $\mathbb{1}\otimes\sigma_{x}$ & $\sigma_{z}\otimes\sigma_{x}$ & $(1, 1, 0, 0)$ & $(1, -1, 0, 0)$ & $(0, 0, 1, 1)$ & $(0, 0, 1, -1)$ \\
$\sigma_{z}\otimes\sigma_{z}$ & $\sigma_{x}\otimes\sigma_{x}$ & $\sigma_{y}\otimes\sigma_{y}$ & $(0, 1, 1, 0)$ & $(0, 1, -1, 0)$ & $(1, 0, 0, 1)$ & $(1, 0, 0, -1)$ \\
\end{tabular} 
\end{ruledtabular}

@@

Since observables in equation~(\ref{eq:MerminSquare}) are not projections,
if we want to reformulate the above argument in the language of quantum
probability measures, we first need to find the common eigenbasis
of each row and column, and consider the projections to each eigenvectors.
Let $\mathcal{T}_{24}$ denote all eigenstates listed in table~\ref{table:commonBasis}.
The Kochen-Specker theorem could then be proved by showing there is
no function~$v:\events_{24}\rightarrow\left\{ 0,1\right\} $ satisfying
equation~(\ref{eq:Kochen-Specker-Rules}), where 
\begin{equation}
\events_{24}=\set{\sum_{i=1}^{N}\proj{\psi_{i}}}{\textrm{mutually orthogonal }\left\{ \ket{\psi_{i}}\right\} _{i=1}^{N}\subseteq\mathcal{T}_{24}}
\end{equation}
which is a sub-event space defined in definition~\ref{def:sub-event-space}.
This kind of $v$ is actually a quantum cryptodeterministic measure.
Since a cryptodeterministic measure is a special case of real-valued
probability measure, by theorem~\ref{lemma:classical-probability-measures},
the quantum cryptodeterministic measure~$v$ exists if and only if
there exists a frame function~$f:\mathcal{T}_{24}\rightarrow\left\{ 0,1\right\} $
which should at least satisfy
\begin{subequations}
\label{eq:Kernaghan-1}
\begin{eqnarray}
1 & = & f(1, 0, 0, 0) + f(0, 1, 0, 0) + f(0, 0, 1, 0) \nonumber \\*
  &   & + f(0, 0, 0, 1) \textrm{ and} \\
1 & = & f(-1, 1, 1, 1) + f(1, -1, 1, 1) + f(1, 1, -1, 1) \nonumber \\*
  &   & + f(1, 1, 1, -1)
\end{eqnarray}
\end{subequations}
because of table~\ref{table:commonBasis}. $f$ should also satisfy
the following equations since the vectors in each equation form an
orthogonal basis~\cite{Kernaghan1994,peres1995quantum}:
\begin{subequations}
\label{eq:Kernaghan-2}
\begin{eqnarray}
1 & = & f(1, 0, 0, 0) + f(0, 1, 0, 0) + f(0, 0, 1, 1) \nonumber \\*
  &   & + f(0, 0, 1, -1)\textrm{ ,}\\
1 & = & f(1, 0, 0, 0) + f(0, 0, 1, 0) + f(0, 1, 0, 1) \nonumber \\*
  &   & + f(0, 1, 0, -1)\textrm{ ,}\\
1 & = & f(1, 0, 0, 0) + f(0, 0, 0, 1) + f(0, 1, 1, 0) \nonumber \\*
  &   & + f(0, 1, -1, 0)\textrm{ ,}\\
1 & = & f(-1, 1, 1, 1) + f(1, 1, -1, 1) + f(1, 0, 1, 0) \nonumber \\*
  &   & + f(0, 1, 0, -1)\textrm{ ,}\\
1 & = & f(-1, 1, 1, 1) + f(1, 1, -1, 1) + f(0, 1, 1, 0) \nonumber \\*
  &   & + f(1, 0, 0, -1)\textrm{ ,}\\
1 & = & f(1, 1, -1, 1) + f(1, 1, 1, -1) + f(0, 0, 1, 1) \nonumber \\*
  &   & + f(1, -1, 0, 0)\textrm{ ,}\\
1 & = & f(0, 1, -1, 0) + f(1, 0, 0, -1) + f(1, 1, 1, 1) \nonumber \\*
  &   & + f(1, -1, -1, 1)\textrm{ ,}\\
1 & = & f(0, 0, 1, -1) + f(1, -1, 0, 0) + f(1, 1, 1, 1) \nonumber \\*
  &   & + f(1, 1, -1, -1)\textrm{ ,}\\
1 & = & f(1, 0, 1, 0) + f(0, 1, 0, 1) + f(1, 1, -1, -1) \nonumber \\*
  &   & + f(1, -1, -1, 1)\textrm{ .}
\end{eqnarray}
\end{subequations}
In equation~\ref{eq:Kernaghan-1} and \ref{eq:Kernaghan-2}, there
are odd number of equations, but each $f\left(\alpha_{0},\alpha_{1},\alpha_{2},\alpha_{3}\right)$
occurs twice. Therefore, there is no frame function~$f:\mathcal{T}_{24}\rightarrow\left\{ 0,1\right\} $
satisfying equation~\ref{eq:Kernaghan-1} and \ref{eq:Kernaghan-2}.

>>>>

On the other hand, Gleason's theorem can be expressed as the limiting
case when the collection of intervals are all singletons~$\mathscr{I}_{\infty}=\set{\left[x,x\right]}{x\in\left[0,1\right]}$.
In the next paragraph, we will show the Kochen-Specker theorem~\citep{kochenspecker1967,peres1995quantum,Redhead1987-REDINA}
is another limiting case when the collection of intervals are $\mathscr{I}_{\mathrm{D}}=\left\{ \imposs,\necess\right\} $,
where $\imposs=\left[0,0\right]$ and $\necess=\left[1,1\right]$.

@@

The Kochen-Specker theorem asserts that there is no function~$v$
assigning a definitely value to all observables such that \begin{subequations}
\label{eq:Kochen-Specker-Rules} 
\begin{eqnarray}
 &  & v\left(O_{1}\right)+v\left(O_{2}\right)=v\left(O_{1}+O_{2}\right)\textrm{ and}\\
 &  & v\left(O_{1}\right)v\left(O_{2}\right)=v\left(O_{1}O_{2}\right)
\end{eqnarray}
\end{subequations} if $O_{1}$ and $O_{2}$ are commuting observables.
Suppose that there is a function~$v$ satisfying these two properties,
it must send an observable to its eigenvalues so that the following
observables~\citep{Mermin1990Simple,peres1995quantum}: 
\begin{equation}
\begin{array}{ccc}
\mathbb{1}\otimes\sigma_{z} & \sigma_{z}\otimes\mathbb{1} & \sigma_{z}\otimes\sigma_{z}\\
\sigma_{x}\otimes\mathbb{1} & \mathbb{1}\otimes\sigma_{x} & \sigma_{x}\otimes\sigma_{x}\\
\sigma_{x}\otimes\sigma_{z} & \sigma_{z}\otimes\sigma_{x} & \sigma_{y}\otimes\sigma_{y}
\end{array}\label{eq:MerminSquare}
\end{equation}
must be sent to $1$ or $-1$. In each row and column, operators commutes,
and each operator is the product of the two others, except in the
third column $\left(\sigma_{z}\otimes\sigma_{z}\right)\left(\sigma_{x}\otimes\sigma_{x}\right)=-\sigma_{y}\otimes\sigma_{y}$.
Therefore, it is clear impossible to find a function~$v$ such that
\begin{equation}
\begin{array}{ccc}
v\left(\mathbb{1}\otimes\sigma_{z}\right) & v\left(\sigma_{z}\otimes\mathbb{1}\right) & v\left(\sigma_{z}\otimes\sigma_{z}\right)\\
v\left(\sigma_{x}\otimes\mathbb{1}\right) & v\left(\mathbb{1}\otimes\sigma_{x}\right) & v\left(\sigma_{x}\otimes\sigma_{x}\right)\\
v\left(\sigma_{x}\otimes\sigma_{z}\right) & v\left(\sigma_{z}\otimes\sigma_{x}\right) & v\left(\sigma_{y}\otimes\sigma_{y}\right)
\end{array}\label{eq:MerminSquare-values}
\end{equation}
satisfying equation~(\ref{eq:Kochen-Specker-Rules}).

\begin{table*}
\caption{\label{table:commonBasis}In each row, three observables are listed
in the left column commutes, and their common eigenbasis is listed
in the right column. In order to unified and simplify notation, we
do not normalize eigenstates, and represent the state~$\alpha_{0}\ket{0}+\alpha_{1}\ket{1}+\alpha_{2}\ket{2}+\alpha_{3}\ket{3}$
as $\left(\alpha_{0},\alpha_{1},\alpha_{2},\alpha_{3}\right)$.}

\begin{ruledtabular}
\begin{tabular}{ccc|cccc}
\multicolumn{3}{c}{Commuting observables} & \multicolumn{4}{c}{Common eigenbasis}\tabularnewline
\hline 
$\mathbb{1}\otimes\sigma_{z}$  & $\sigma_{z}\otimes\mathbb{1}$  & $\sigma_{z}\otimes\sigma_{z}$  & $(1,0,0,0)$  & $(0,1,0,0)$  & $(0,0,1,0)$  & $(0,0,0,1)$ \tabularnewline
$\sigma_{x}\otimes\mathbb{1}$  & $\mathbb{1}\otimes\sigma_{x}$  & $\sigma_{x}\otimes\sigma_{x}$  & $(1,1,1,1)$  & $(1,-1,1,-1)$  & $(1,1,-1,-1)$  & $(1,-1,-1,1)$ \tabularnewline
$\sigma_{x}\otimes\sigma_{z}$  & $\sigma_{z}\otimes\sigma_{x}$  & $\sigma_{y}\otimes\sigma_{y}$  & $(1,1,1,-1)$  & $(1,1,-1,1)$  & $(1,-1,1,1)$  & $(-1,1,1,1)$ \tabularnewline
$\mathbb{1}\otimes\sigma_{z}$  & $\sigma_{x}\otimes\mathbb{1}$  & $\sigma_{x}\otimes\sigma_{z}$  & $(1,0,1,0)$  & $(0,1,0,1)$  & $(1,0,-1,0)$  & $(0,1,0,-1)$ \tabularnewline
$\sigma_{z}\otimes\mathbb{1}$  & $\mathbb{1}\otimes\sigma_{x}$  & $\sigma_{z}\otimes\sigma_{x}$  & $(1,1,0,0)$  & $(1,-1,0,0)$  & $(0,0,1,1)$  & $(0,0,1,-1)$ \tabularnewline
$\sigma_{z}\otimes\sigma_{z}$  & $\sigma_{x}\otimes\sigma_{x}$  & $\sigma_{y}\otimes\sigma_{y}$  & $(0,1,1,0)$  & $(0,1,-1,0)$  & $(1,0,0,1)$  & $(1,0,0,-1)$ \tabularnewline
\end{tabular}
\end{ruledtabular}

@@

Since observables in equation~(\ref{eq:MerminSquare}) are not projections,
if we want to reformulate the above argument in the language of quantum
IVPMs, we first need to find the common eigenbasis of each row and
column, and consider the projections to each eigenvectors~\citep{Kernaghan1994,peres1995quantum}.
Let $\mathcal{T}_{24}$ denote all eigenstates listed in table~\ref{table:commonBasis}.
The Kochen-Specker theorem could then be proved by showing there is
no function~$v:\events_{24}\rightarrow\left\{ 0,1\right\} $ satisfying
equation~(\ref{eq:Kochen-Specker-Rules}), where 
\begin{equation}
\events_{24}=\set{\sum_{i=1}^{N}\proj{\psi_{i}}}{\begin{gathered}\textrm{mutually orthogonal }\\
\left\{ \ket{\psi_{i}}\right\} _{i=1}^{N}\subseteq\mathcal{T}_{24}
\end{gathered}
}
\end{equation}
is a sub-event space.

Assume there is a function~$v:\events_{24}\rightarrow\left\{ 0,1\right\} $
satisfying equation~(\ref{eq:Kochen-Specker-Rules}). There must
be a quantum IVPM~$\bar{\mu}:\events_{24}\rightarrow\mathscr{I}_{\mathrm{D}}$
defined by $\bar{\mu}\left(P\right)=\iota_{0}\left(v\left(P\right)\right)$,
where 
\begin{equation}
\iota_{0}\left(x\right)=\begin{cases}
\necess & \text{ if}x=1\text{ ;}\\
\imposs & \text{ if}x=0\text{ .}
\end{cases}\label{eq:homomorphism-0}
\end{equation}
Hence, there exists an interval-valued frame function~$\bar{f}:\mathcal{T}_{24}\rightarrow\mathscr{I}_{\mathrm{D}}$
defined by $\bar{f}\left(\ket{\psi}\right)=\bar{\mu}\left(\proj{\psi}\right)$.
Because of Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion}),
we have\begin{subequations} \label{eq:Kernaghan} 
\begin{eqnarray}
\necess & \subseteq & \bar{f}(1,0,0,0)+\bar{f}(0,1,0,0)+\bar{f}(0,0,1,0)\nonumber \\*
 &  & +\bar{f}(0,0,0,1)\textrm{ ,}\\
\necess & \subseteq & \bar{f}(-1,1,1,1)+\bar{f}(1,-1,1,1)+\bar{f}(1,1,-1,1)\nonumber \\
 &  & +\bar{f}(1,1,1,-1)\textrm{ ,}\\
\necess & \subseteq & \bar{f}(1,0,0,0)+\bar{f}(0,1,0,0)+\bar{f}(0,0,1,1)\nonumber \\
 &  & +\bar{f}(0,0,1,-1)\textrm{ ,}\\
\necess & \subseteq & \bar{f}(1,0,0,0)+\bar{f}(0,0,1,0)+\bar{f}(0,1,0,1)\nonumber \\*
 &  & +\bar{f}(0,1,0,-1)\textrm{ ,}\\
\necess & \subseteq & \bar{f}(1,0,0,0)+\bar{f}(0,0,0,1)+\bar{f}(0,1,1,0)\nonumber \\*
 &  & +\bar{f}(0,1,-1,0)\textrm{ ,}\\
\necess & \subseteq & \bar{f}(-1,1,1,1)+\bar{f}(1,1,-1,1)+\bar{f}(1,0,1,0)\nonumber \\*
 &  & +\bar{f}(0,1,0,-1)\textrm{ ,}\\
\necess & \subseteq & \bar{f}(-1,1,1,1)+\bar{f}(1,1,-1,1)+\bar{f}(0,1,1,0)\nonumber \\*
 &  & +\bar{f}(1,0,0,-1)\textrm{ ,}\\
\necess & \subseteq & \bar{f}(1,1,-1,1)+\bar{f}(1,1,1,-1)+\bar{f}(0,0,1,1)\nonumber \\*
 &  & +\bar{f}(1,-1,0,0)\textrm{ ,}\\
\necess & \subseteq & \bar{f}(0,1,-1,0)+\bar{f}(1,0,0,-1)+\bar{f}(1,1,1,1)\nonumber \\*
 &  & +\bar{f}(1,-1,-1,1)\textrm{ ,}\\
\necess & \subseteq & \bar{f}(0,0,1,-1)+\bar{f}(1,-1,0,0)+\bar{f}(1,1,1,1)\nonumber \\*
 &  & +\bar{f}(1,1,-1,-1)\textrm{ ,}\\
\necess & \subseteq & \bar{f}(1,0,1,0)+\bar{f}(0,1,0,1)+\bar{f}(1,1,-1,-1)\nonumber \\*
 &  & +\bar{f}(1,-1,-1,1)\textrm{ .}
\end{eqnarray}
\end{subequations}\newpage{}

In equation~\ref{eq:Kernaghan}, there are odd number of equations,
but each $f\left(\alpha_{0},\alpha_{1},\alpha_{2},\alpha_{3}\right)$
occurs twice. Therefore, there is no frame function~$f:\mathcal{T}_{24}\rightarrow\left\{ 0,1\right\} $
satisfying equation~\ref{eq:Kernaghan} and \ref{eq:Kernaghan-2}.
